\documentclass{article}
\usepackage[a4paper, left=2cm, right=2cm, top=2cm, bottom=2cm,textwidth=17cm,textheight=23cm]{geometry}
\usepackage{xeCJK}
\usepackage{setspace}
\usepackage{fontspec}
\usepackage{fancyhdr}
\usepackage{hyperref}
\usepackage{xcolor}
\setCJKmainfont{標楷體-繁}
\setmainfont{Times New Roman}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot[C]{\textsf{\thepage}}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\title{\fontsize{16pt}{16pt}\selectfont Australia Politics}
\author{}
\date{}
\begin{document}
\setstretch{1.05}
\maketitle
\fontsize{14pt}{14pt}\selectfont
\begin{flushleft}
Instructor Information
\end{flushleft}
\begin{itemize}
\item Instructor: Dr. Tzu-Chi Hsiao. \\
\item Office: Room 506, Department of Political Science. \\
\item Office hours: 08:20-09:10, Every Wednesday. \\
\item Email: \href{mailto:politics.tchsiao@gmail.com}{politics.tchsiao@gmail.com}. \\
\item Webpage: \href{https://politics-tchsiao.github.io/website/}{https://politics-tchsiao.github.io/website/}. \\
\end{itemize}
Course Information \\
\begin{itemize}
\item Course: Australia Politics. \\
\item Credit: 3. \\
\item Hours: 09:20-12:10, Every Thursday. \\
\item Prerequisite: Communism Theory. \\
\item Webpage: \href{https://politics-tchsiao.github.io/au\_politics/}{https://politics-tchsiao.github.io/au\_politics/}. \\
\item Course description \\
This is a course for my researchers. \\
\item Course objectives \\
1. To understand the basic concepts of each ideologies. \\
2. To understand the basic concepts of each solutions. \\
3. To understand the basic concepts of each political systems. \\
\end{itemize}
\newpage
\begin{flushleft}
Grading \\
\end{flushleft}
\begin{itemize}
\item Presentation: 100\%. \\
\end{itemize}
Textbook \\
\begin{itemize}
\item Lecturer notes by Dr. Tzu-Chi Hsiao. \\
\end{itemize}
Course Schedule \\
\begin{itemize}
\item Please refer to the \href{https://politics-tchsiao.github.io/au\_politics/}{course webpage}. \\
\end{itemize}
\end{document}
